The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-27 paper.tex
update

\section{Introduction}

@@

  The governing equations solving the special relativistic ideal fluid\
  including CR advection, and dynamical coupling between the thermal gas and CRs without CR diffusion\
  turn out to be

@@

  \begin{enumerate}
     \item  We multiply $f(\bold{x})$ and $\rho_{\text{isoDisk}}(z)$\
            to obtain the density of disk $\tilde{\rho}_{\text{ismDisk}}(\bold{x})$. i.e.\
            $\displaystyle\tilde{\rho}_{\text{ismDisk}}(\bold{x}) =\
            f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
            The temperature is determined by
            $\displaystyle \tilde{T}_{\text{ismDisk}} = T_{\text{isoDisk}}\rho_{\text{isoDisk}}/\tilde{\rho}_{\text{ismDisk}}$.
     \item  If $\tilde{T}_{\text{ismDisk}}$ larger than $T_{\text{crit}}$,
  \end{enumerate}

  The porosity of the disk arises by imposing an upper temperature cutoff for the\
  existence of clouds at $T_{\text{crit}} = 10^{4}$ K, beyond which clouds
  are deemed thermally unstable and replaced by temperature of atmosphere.

  The temperature in each cell within the disk is determined by pressure equilibrium with hot gas.\
  The clouds within the disk are in pressure equilibrium with the surrounding hot voids, thus\
  $\displaystyle T_{\text{ismDisk}} = T_{\text{isoDisk}}\rho_{\text{isoDisk}}/\rho_{\text{ismDisk}}$.

  We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.
  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
  for constructing clumpy structure, and we do not repeat here.

  When the warm gas temperature exceeds $T_{\text{crit}}=$ K, it is deemed to be thermally unstable and is replaced\
  by hot gas. This makes the gas porous.

%  \begin{enumerate}
%     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(z)$ by \Cref{isothermal-disk-density}.
%     \item Using PyFC code to obtain a dimensionless clumpy distribution $f$ obeying\
%           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
%     \item \Cref{density-ism-disk}.
%     \item
%  \end{enumerate}

>>>>

\section{Introduction}
Early attempts to model the Fermi bubbles assumed that the jet is vertial to the Galactic plane...

@@

  The governing equations solving the special relativistic ideal fluid\
  including CR advection, and dynamical coupling between the thermal gas and CRs without CR diffusion\
  can be written a succinct form as

@@

  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
  for constructing a clumpy scalar field, and we do not repeat here.

  The density of clumpy disk can thus be obtained by taking the scalar products of\
  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disk:\
  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
  f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
  Also, the pressure equilibrium condition implies that the temperature of disk is
  $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$.

  Moreover, as the clouds are considered to be thermally unstable\
  when the cloud temperature beyond\
  the critical temperature of the warm atomic phase.\
  We replace the cell density with\
  $\rho_{\text{ismDisk}}T_{\text{ismDisk}}/T_{\text{atmp}}$\
  for a cell temperature greater than the critical value $T_{\text{crit}}$.

  %Doing so, the porosity of the disk can arises,\

  We summarize the parameters of clumpy disk and their references in \Cref{table-parameters}.
